Flowchart of Current Algorithm

### 2012-07-17 docs/flowchart/flowchart.tex
more descriptions of the initialization

\item {\bf Do} {$\nu = 1,...,N_{\rm iters}^{S}$.}
  \begin{enumerate}

@@

Next, we need to construct approximations to $\etarho^{-\myhalf}, \psi^{-\myhalf}, S^1$,
and $\pi^{-\myhalf}$.  As initial approximations, set 
$\etarho^{-\myhalf}=0, \psi^{-\myhalf}=0, S^{1,0}=S^0$, and $\pi^{-\myhalf}=0.$
\begin{enumerate}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}
\renewcommand{\labelenumii}{\roman{enumii}.}
\addtocounter{enumi}{1}
\item {\bf Do} {$\nu = 1,...,N_{\rm iters}^{\pi}$.}
  \begin{enumerate}
  \item Perform {\bf Steps 1-11} as described above, using 
    $S^{\myhalf,\star\star} = (S^0 + S^{1,\nu-1})/2$ in {\bf Step 2} as described.
    The only other difference in the time advancement is that in {\bf Step 11}
    we define ${\bf V} = (\Ubt^{1,\star} - \Ubt^0)$ and solve
    \begin{equation}  L_\beta^\rho \phi = D \left ( \beta_0^{\myhalf} {\bf V} \right) - \beta_0^{\myhalf} \left[ \left(S^{1}-\overline{S^{1}}\right) - \left(S^{0}-\overline{S^{0}}\right) \right] \enskip . 
    \end{equation}
    (The motivation for this form of the projection in the initial pressure iterations
    is discussed in (cite almgren:bell:crutchfield).)
      We discard the new velocity resulting from this, but keep the new  
      value for $\pi^{\myhalf} = \pi^{-\myhalf} + (1 / \dt) \; \phi.$  
      These steps also yield new scalar data at time $\dt,$ which
      we discard, and new values for $\etarho^{\myhalf}$ ({\bf Step 8C}), 
      $\psi^{\myhalf}$ ({\bf Step 8F}), 
      $S^{1,\nu}$ ({\bf Step 10A}), and $\pi^{\myhalf}$ ({\bf Step 11}), which we keep.
    \item Set $\pi^{-\myhalf} = \pi^{\myhalf}$, $\etarho^{-\myhalf} = \etarho^{\myhalf}$,
      and $\psi^{-\myhalf} = \psi^{\myhalf}$. 
    \end{enumerate}

>>>>

\item {\em Initial Projection}: if {\tt do\_initial\_projection = T}, then we 
   first project the velocity field with $\rho = 1$ and $\beta_0^0$ defined 
   from the initial data.  No sources are included in $S$.  The elliptic
   equation we solve is 
   \begin{equation}
   \nabla \cdot \beta_0^0 \nabla \phi = - \nabla \cdot (\beta_0^0 \Ub^0)
   \end{equation}
   This $\phi$ is then used to correct the velocity field.

\item {\em ``Divu'' iterations}: Next we do {\tt init\_divu\_iter} iterations 
  to project the velocity field using a constraint that sees the reactions. 
  The initial timestep estimate is provided by {\tt firstdt}, to allow us to 
  integrate the reaction networks.  In this projection, again the density is 
  set to 1, and the elliptic equation we solve is:
   \begin{equation}
   \nabla \cdot \beta_0^0 \nabla \phi = \beta_0 (S - \Sbar)- \nabla \cdot (\beta_0^0 \Ub^0)
   \end{equation}

  {\bf Do} {$\nu = 1,...,N_{\rm iters}^{S}$.}
  \begin{enumerate}

@@

Next, we need to construct approximations to $\etarho^{-\myhalf}, \psi^{-\myhalf}, S^1$,
and $\pi^{-\myhalf}$.  As initial approximations, set 
$\etarho^{-\myhalf}=0, \psi^{-\myhalf}=0, S^{1,0}=S^0$, and $\pi^{-\myhalf}=0.$
\begin{enumerate}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}
\renewcommand{\labelenumii}{\roman{enumii}.}
\addtocounter{enumi}{2}
\item {\bf Do} {$\nu = 1,...,N_{\rm iters}^{\pi}$.}
  \begin{enumerate}
  \item Perform {\bf Steps 1-11} as described above, using 
    $S^{\myhalf,\star\star} = (S^0 + S^{1,\nu-1})/2$ in {\bf Step 2} as described.
    The only other difference in the time advancement is that in {\bf Step 11}
    we define ${\bf V} = (\Ubt^{1,\star} - \Ubt^0)$ and solve
    \begin{equation}  L_\beta^\rho \phi = D \left ( \beta_0^{\myhalf} {\bf V} \right) - \beta_0^{\myhalf} \left[ \left(S^{1}-\overline{S^{1}}\right) - \left(S^{0}-\overline{S^{0}}\right) \right] \enskip . 
    \end{equation}
    (The motivation for this form of the projection in the initial pressure iterations
    is discussed in (cite almgren:bell:crutchfield).)
      We discard the new velocity resulting from this, but keep the new  
      value for $\pi^{\myhalf} = \pi^{-\myhalf} + (1 / \dt) \; \phi.$  
      These steps also yield new scalar data at time $\dt,$ which
      we discard, and new values for $\etarho^{\myhalf}$ ({\bf Step 8C}), 
      $\psi^{\myhalf}$ ({\bf Step 8F}), 
      $S^{1,\nu}$ ({\bf Step 10A}), and $\pi^{\myhalf}$ ({\bf Step 11}), which we keep.
    \item Set $\pi^{-\myhalf} = \pi^{\myhalf}$, $\etarho^{-\myhalf} = \etarho^{\myhalf}$,
      and $\psi^{-\myhalf} = \psi^{\myhalf}$. 
    \end{enumerate}
